|

### 2021-03-17 documentation/readme.Rmd
Editted poll of polls section

As of `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`, **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "has", "have")` the largest base of support** at around `r paste0(txt_dta$share[1], " (95% CI: ", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")` of the electorate. **They hold a lead over the `r txt_dta$party[2]`** of `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (95% CI: ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`. **This puts the `r txt_dta$party[2]` in second place** on `r paste0(txt_dta$share[2], " (95% CI: ", txt_dta$lower[2], " to ", txt_dta$upper[2], ")")` of the vote. **The `r txt_dta$party[3]` are in third place** with the support of `r paste0(txt_dta$share[3], " (95% CI: ", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")` of voters.

>>>>

**British Poll of Polls, `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`:**

- **`r txt_dta$party[1]`:** `r paste0(txt_dta$share[1], " (95% CI: ", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")`
- **`r txt_dta$party[2]`:** `r paste0(txt_dta$share[2], " (95% CI: ", txt_dta$lower[2], " to ", txt_dta$upper[2], ")")`
- **`r txt_dta$party[3]`:** `r paste0(txt_dta$share[3], " (95% CI: ", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")`

As of `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`, **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "is", "are")` the largest party**. **They hold a lead over the `r txt_dta$party[2]`** of `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (95% CI: ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`. **This puts the `r txt_dta$party[2]` in second place** and **the `r txt_dta$party[3]` in third place**.
